cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Updated additional functions table

```{r}
add_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_bkgnoise",
                            "randomize_rows",
                            "gen_nproduct",
                            "gen_nsum",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3",
                            "gen_rotation",
                            "gen_globalminmax",
                            "scale_data"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
add_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_bkgnoise",
                            "randomize_rows",
                            "gen_nproduct",
                            "gen_nsum",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3",
                            "gen_rotation",
                            "normalize_data"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```
